sensi_an_rotations201911. To analyse rotation runs for paper

### 2019-11-13 inst/documents/rotations_notes.Rmd
correcting couple bugs insecticide switching
starting plots for paper
investigating strange model behaviour

@@

see why insecticide_check() is failing for mort

~ work out what we want Sam to do
~~ do 16 sets of 10,000 runs
~~ what analyses on outputs

>>>>

I think I fixed this issue ...?

# 6/11/2019

starting to get some of the analysis code ready for Sam.

taking code from sensi_an_rotations1.Rmd

# 13/11/2019

Why does this sequence switch back when there is no cost or dispersal ?

run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0021, cost=c(0), eff=c(0.98), dom_sel=c(0.51),dom_cos=c(0.63), rr=c(0.8), expo_hi=0.47, male_expo_prop=0.01, coverage=1, migration=0,min_rwr_interval=10, diagnostics = TRUE)

Using a mortality switch it now doesn't switch back :
run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0021, cost=c(0), eff=c(0.98), dom_sel=c(0.51),dom_cos=c(0.63), rr=c(0.8), expo_hi=0.47, male_expo_prop=0.01, coverage=1, migration=0, min_rwr_interval=10, mort_or_freq = 'mort')

Not due to dom_cos >0 even though cost=0.

insecticide1 check=0.488229891221731 freq=0.488229891221731 surv=0.406690062481814 gens_this_insecticide=39
generation 41

insecticide1 check=0.520515732451062 freq=0.520515732451062 surv=0.431997734603674 gens_this_insecticide=40
change from insecticide1 check=0.520515732451062

generation 121, switch from insecticide 3 to 1; new frequency vs threshold = 0.488603 and 0.500000

Seems like freq has declined from 0.5205 to 0.4886 while insecticide not in use despite no costs or dispersal ???

ooo weird seems to go down the generation after use stopped and then stays at that constant level:

gen39 i1 freq=0.455590826478509
gen40 i1 freq=0.488229891221731
gen41 i1 freq=0.520515732451062
gen42 i1 freq=0.488603067950344
gen43 i1 freq=0.488603067950344
gen44 i1 freq=0.488603067950344

@@

1. find & fix problem with C runs see above
2. implement annual restrictions for sequences

# I think we allow sequence to exit at anytime ? This gives a kind of advantage to sequences, rotations tend to end up with more generations above threshold.

Questions to answer re 16k runs :

1. why with mortality switch are there more runs favouring sequence ?

### 2019-11-13 inst/documents/sensi_an_rotations201911.Rmd
investigating strange model behaviour

@@

df_res_16$rms_percent <- 100 * df_res_16$rot_minus_seq / df_res_16$gens_seq

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_pcent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("percentage advantage of rotations over sequence in generations") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

>>>>

# calc percentage difference between rotation and sequence
df_res_16$rms_percent <- 100 * df_res_16$rot_minus_seq / df_res_16$gens_seq

@@

# OR use a % threshold for strategies to be the same
# still uses widthbin which now represents a pcent
# no_difference set to +/- half of widthbin% set above
df_res_16$best_strategy <- ifelse(df_res_16$rms_percent <= -(widthbin/2),"sequence", ifelse(df_res_16$rms_percent > (widthbin/2), "rotation", "no_difference"))

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
#TODO make the best_strategy threshold basedon percent too
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("percentage advantage of rotations over sequence in generations") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))
